\textbf{ \Large{Decentralized, autonomous sensor fault detection using neural networks}}

### 2015-01-17 Paper/PaperJahrSchlich.tex
cleaned up a little
Überarbeitung Abschnitt SHM, UML/Java fehlt

%The next command sets up an environment for the abstract to your paper.
\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}

@@

%1st Draft:
%The dependability and the accuracy of structural health monitoring systems are significantly affected by sensor faults. Autonomous fault detection can be obtained by comparing sensor data with data predicted by neural networks. In this paper, the design and implementation of a wireless structural health monitoring system capable of autonomous sensor fault detection using a neural network is presented. The system was validated in laboratory experiments showing its efficency.

%2nd Draft
%The dependability and the accuracy of structural health monitoring systems are significantly affected by sensor faults. In this paper, the design and implementation of a wireless structural health monitoring system is presented. A neural network is used for autonomous fault detection by comparing the predicted data with measured sensor data. In laboratory experiments, sensor faults were detected reliably, proving that the use of neural networks increases the reliability of structural health monitoring systems.

%3th Draft 
%The dependability and the accuracy of structural health monitoring systems are significantly affected by sensor faults. In this paper, the design and implementation of a wireless structural health monitoring system, capable of autonomous fault detection, is presented. A neural network is used for self-monitoring of each sensor by predicting data values and comparing these values to measured sensor data. In laboratory experiments, sensor faults were detected reliably, proving that the use of neural networks increases the reliability of structural health monitoring systems.

%4th Draft
%The dependability and the accuracy of structural health monitoring systems are significantly affected by sensor faults. 
%In this paper, the design and implementation of a wireless structural health monitoring system, capable of autonomous fault detection, is presented. 
%A neural network is used for self-monitoring of each sensor node by predicting the measured data with data values submitted by adjacent sensor nodes. 
%These predictions are then compared to the measured data.
%In laboratory experiments, sensor faults were detected, proving that the use of neural networks increases the reliability of structural health monitoring systems.

@@

\begin{tabular}{|l|l|}
\hline 
Sensorknoten (SunSPOT) & sensor node \\ 
\hline 
einzelner Messsensor (Thermometer) & sensor \\ 
\hline 
Knoten im neuronalen Netz & neuron \\ 
\hline 
eine abgeschlossene Messung & measurement \\ 
\hline 
gemessene Werte & sensor data \\ 
\hline 
vorhergesagte Werte & predicted data \\ 
\hline 
durch Vorhersage erwartete Werte & expected data \\ 
\hline 
einzelner Messwert & measurement value \\ 
\hline 
\end{tabular}

\todo[inline]{"tatsächliche" / reale; virtuelle Messung?}

@@

%\begin{itemize}
%\item Unfälle gefährden Menschenleben und sind teuer
%\item SHMS können Unfälle verhindern
%\item kabellose Sensoren sind besser
%\item Sensoren sind fehleranfällig
%\item Lösung: autonome Fehlererkennung 
%\item Lösungsansätze mit Literaturbelegen
%\item Ansatz: Neuronales Netz
%\item Überblick, Vorteile
%\item Literatur zu neuronalen Netzen
%\item Überblick über geleistete Arbeit
%\end{itemize}
%
%\newpage
%
%Civil engineering structures are designed to resist extensive external impact over several decades. 
%Over time, the structural stability can decrease to an hazardous level. 
%To prevent structural failure, demolition and replacement of the building or rehabilitation and repair works have to be considered.
%From the outside, it is hard to determine whether building structures are damaged.
%To decide whether cost- and scheduling-intensive strengthening actions are required and to predict failure in advance, structural health monitoring (SHM) is used.
%
%\cite[4]{BisbySHM} defines SHM as "a non-destructive \textit{in-situ} structural evaluation method that uses any of several sensors which are attached to, or embedded in, a structure". 
%The obtained sensor data is "collected, analyzed and stored".
%The structure is observed over long periods of time - up to several years - using data obtained by sensor nodes attached to the \textbf{construction}.
%Via analyzing the measured data, such as acceleration or strain, changes in material and geometric behaviour can be recognized early on.
%
%
%((((
%
%Traditionally, the used sensor nodes are wired with optical fiber cables. 
%However, using wired SHM systems has several disadvantages: 
%For monitoring large constructions like bridges or high-rise buildings, many sensor nodes and therefore a big amount of wire is needed, raising material and personnel expenses.
%Optimal positions for sensor nodes can be impossible to wire and clamps can damage the facade. 
%Visible wires compromise the aesthetic view of a construction and draw interest to vandalism.
%
%))))
%
%Wireless SHM systems are composed of a several sensor nodes, a base station and a personal computer, that communicate by radio. 
%Therefore, the named disadvantages of cables do not apply.
%Wireless SHM, however, bear some challenges that have to be considered. 
%Electricity supply is constrained to battery life or expensive alternative power suppliers.
%The transmitter signal strength has to be optimized to span long distances without disturbing nearby electronic devices or humans.
%Data security may have to be ensured by encrypting the transmitted data and eliminating the possibility of data manipulation.In this case
%When using several different sensor nodes, the timestamps of single measurement values can differ. 
%To assure the relatability of the sensor data, it is therefore necessary to synchronize all sensor timers. 
%
%Over time, sensors can break and become faulty. Faults can be due to either sudden failure or gradually loss of accuracy.
%To ensure the dependability and the accuracy of the structural health monitoring system, these sensor faults must be detected and eliminated in real time. 
%
%To autonomously detect sensor faults, several different approaches have been tested.
%
%...
%
%\todo[inline]{Literatur zu nicht neuronalen netzwerken und deren Probleme}
%
%\todo[inline]{neuronale Netze. später Abgleich mit Abschnitt.}
%
%This paper shows a wireless structural health monitoring system with autonomous fault detection. 
%At first, the SHM system is designed and implemented. 
%Next, a neural network is implemented in each sensor and trained to detect faulty behaviour. 
%The system is then tested in laboratory experiments. 
%Finally, the experimental results are analyzed and future research directions proposed.

@@

\section*{Design and implementation of the wireless structural health monitoring system}

\textbf{1. paragraph: SHM general}

\begin{itemize}
\item wireless SHM system consits of nodes and base station
\item nodes collect data, and process data
\item processed data is sent to base station and personal computer
\item data is stored in database
\end{itemize}

@@

Task 1. to 3. are implemented on the building site, tasks 4. to 6. at a workstation. 
A wireless SHM system installed on the building site consists of sensor nodes attached to the construction, a base station and a local computer. 
The base station, which can be an external device or a computer program, links the individual sensor nodes with each other and the local computer.
To each sensor node, several sensors measuring different physical quantities may be connected. 
During a measurement, the sensor nodes acquire sensor data and may perform initial processing.
The processed data is then transmitted via radio to the base station and, from there, to the local computer. 
At the computer, the data gets stored accessible and save, e. g. in a database for analysis and diagnosis.

\todo[inline]{vielleicht eine Abbildung?}

\textbf{2. paragraph: SunSPOTs}

\begin{itemize}
\item SunSPOTs...
\item several sensors: acc, temp, light...
\item wireless communication
\item base station
\end{itemize}

@@

\begin{figure}[h]
    \centering
    \includegraphics{figures/neuralnetworks.pdf}
    \caption{Schematic drawing of an artificial neural network with three layers}
    \label{fig:neuralnetwork}
\end{figure}
\todo[inline]{Grafik kann nacher noch an unser neuronales Netz angepasst werden}

@@

\textbf{1. paragraph: test setting}

@@

\item learning phase
\end{itemize}

@@

\begin{itemize}
\item excitation
\item sensors start measuring
\item sensor nodes \textbf{perform fft} - what is fft
\item sensor nodes exchange frequencies
\item neural networks check integrity
\item if no faults detected, sensor nodes send data to base station
\end{itemize}

\textbf{3. paragraph: sensor fault}

>>>>

%The next command sets up an environment for the abstract to your paper.
\newenvironment{sciabstract}{%
\begin{quote} \bfseries}
{\end{quote}}

@@

@@

\begin{tabular}{|l|l|}
\hline 
Sensorknoten (SunSPOT) & sensor node \\ 
\hline 
einzelner Messsensor (Thermometer) & sensor \\ 
\hline 
Knoten im neuronalen Netz & neuron \\ 
\hline 
eine abgeschlossene Messungreihe & test run \\ 
\hline 
gemessene Werte & sensor data \\ 
\hline 
vorhergesagte Werte & predicted data \\ 
\hline 
durch Vorhersage erwartete Werte & expected data \\ 
\hline 
einzelner Messwert & measurement \\ 
\hline 
Test & laboratory experiments\\ 
\hline
tatsächliche, nicht virtuelle Messung & actual measurement \\
\hline
Messaufbau & test setup \\
\hline

\end{tabular}

@@

@@

\section*{Design and implementation of the wireless structural health monitoring system}
In the following section, a brief descriptions of SHM systems general is given. Furthermore, the used wireless SHM system is introduced and the Java implementation is described.

@@

Tasks 1 to 3 are usually implemented on site, while tasks 4 to 6 are usually implemented on computer systems off site.
A wireless SHM system installed on the building site consists of sensor nodes attached to the construction, a base station, and a local computer. 
The base station, which can be an external device or a computer program, links the individual sensor nodes with each other and the local computer.
To each sensor node, several sensors measuring different physical quantities may be connected. 
In this project, the acceleration is measured using wireless sensor nodes and a basestation of the type "Oracle Sun SPOT". 
The 3-axis digital output accelerometer with sensitivity ranging between $ \pm $ 2G and $\pm$ 8G has a maximum sample rate of 125Hz. \cite[9]{eDemo2010}

In operation, the sensor nodes acquire sensor data and may perform initial processing.
The processed data is then transmitted via radio to the local computer, where it is stored for analysis and diagnosis.
In this project, the data is transmitted from the sensor nodes to the basestation by radio, and from the basestation to the local computer via USB cable.
On the computer, the data is stored in a MySQL database.

\todo[inline]{vielleicht eine Abbildung? SunSPOTs? Aufbau SHM?}

@@

\begin{figure}[ht]
    \centering
    \includegraphics{figures/neuralnetworks.pdf}
    \caption{Schematic drawing of an artificial neural network with three layers}
    \label{fig:neuralnetwork}
\end{figure}
\todo[inline]{Grafik kann nacher noch an unser neuronales Netz angepasst werden}

@@

\textbf{1. paragraph: test setup}

@@

\end{itemize}

@@

\begin{itemize}
\item learning phase
\item excitation
\item sensors start measuring
\item sensor nodes \textbf{perform fft} - what is fft
\item sensor nodes exchange frequencies
\item neural networks check integrity
\item if no faults detected, sensor nodes send data to base station
\end{itemize}

\textbf{3. paragraph: sensor fault detection}
